---
output:
  word_document: default
  pdf_document: default
  html_document: default
---
title: "Assignment00"
author: "Pavel Makarov"
date: "September 6th, 2023"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

## Add 8 and 5
```{r}
8+5
```
## Subtract 6 from 22
```{r}
6-22
```
## Multiply 6 by 7
```{r}
6*7
```
## Add 4 to 6 and divide the result by 2
```{r}
(4+6)/2
```
## Compute 5 modulo 2
```{r}
5%%2
```
## Assign the value 82 to the variable x
```{r}
x <-  82
```
## Print x
```{r}
x
```
## Assign the value 41 to the variable y
```{r}
y <- 41
```
## Print y
```{r}
y
```
## Assign the output of x + y to the variable z
```{r}
z <- x + y
```
## Print z
```{r}
z
```
## Assign the string value "DSC520" to the variable class_name
```{r}
class_name <- 'DSC520'
```
## Print the value of class_name
```{r}
class_name
```
## Assign the string value of TRUE to the variable is_good
```{r}
is_good <- TRUE
```
## Print the value of is_good
```{r}
is_good
```
## Check the class of the variable is_good using the `class()` function
```{r}
class(is_good)
```
## Check the class of the variable z using the `class()` function
```{r}
class(z)
```
## Check the class of the variable class_name using the class() function
```{r}
class(class_name)
```
